Sparse associative memories

### 2014-06-22 Articles/article.tex
Simulations + correction article.tex

@@

	The analytical result agree with the simulations.

	For one iteration, winner takes all is the same as $a$-winners take all.

>>>>

	gap with density in simulations : under $1$ percent

@@

	The simulations agree with the analytical result.

	For one iteration (for erasures, not for errors), winner takes all is the same as $a$-winners take all.
